\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        % Job Title
        {Lab Technician}
        % Dates
        {Oct. 2024 -- Present}
        % Org.
        {Texas Instruments Innovation Lab at UCF}
        % Location
        {Orlando, FL}
      \resumeItemListStart
        \resumeItem {
            Provided technical guidance on equipment and projects for over 15,000 students and faculty from UCF College of Engineering ranging from freshmen to senior projects.
        }
        \resumeItem{
            Use of subtractive manufacturing such as laser cutting, and additive manufacturing like 3D printing to complete student's academic and personal projects. 
        } 
      \resumeItemListEnd
    \resumeSubheading
        {Math Tutor}
        {Mar. 2024 -- Aug. 2024}
        {Mathnasium}
        {Brandon, FL}
    \resumeItemListStart
        \resumeItem {
            Used adaptive teaching methods to encourage applied problem-solving and mathematical knowledge for 15+ students weekly, resulting in average score improvements of 20\% over 3 months.
        }
        \resumeItem{
            Utilized data entry to track individual student progress across 10+ performance metrics, optimizing personalized lesson plans and improving learning efficiency.
        } 
        % \resumeItem{Demonstrated effective communication with a team of 5 instructors and engaged students in 1-on-1 and small group sessions.}
    \resumeItemListEnd
      \resumeSubheading
        {Hostess}
        {Mar. 2022 - Aug. 2024}
        {Tsunami Sushi and Hibachi Grill}
        {Brandon, FL}
      \resumeItemListStart
        \resumeItem {
            Coordinated seating for 100–150 guests per shift, ensuring efficient table turnover and timely meal preparation during peak dining hours.
        }
        \resumeItem{
             Maintained a clean and welcoming environment by managing dual responsibilities of front-of-house hosting and light maintenance.
        } 
    \resumeItemListEnd
\resumeSubHeadingListEnd